Scheeper's Meager-NWD Game and the Menger Game

### 2014-12-04 phd/dissertation/chapter2.tex
overall cleanup

  If a winning strategy exists for a player $\pl A$ in the game $G$, then we
  write $\pl A \win G$. Otherwise, we write $\pl A \not\win G$.
\end{defn}

@@

If we wish to show that a winning strategy does not exist for a player
(i.e. $\pl A\not\win G$), we
often consider an arbitrary legal strategy, and use it to define a legal
\term{counter-attack} for the opponent. If we can prove that the result of
the game for that strategy and counter-attack is a victory for the opponent,
then a winning strategy does not exist.

@@

\begin{proof}
  $\pl A\win \bakergame{\mathbb{R}}$, since $a_n$ must converge to some
  real number. This implies $\pl B\not\win \bakergame{\mathbb{R}}$, and thus
  $\mathbb{R}$ is not countable.
\end{proof}

@@

\begin{thm}
$\pl E\not\win \bmgame{X}$ if and only if $X$ is a Baire space.
\cite{MR0431104}
\end{thm}

>>>>

  If a winning strategy exists for a player $\pl A$ in the game $G$, then we
  write $\pl A \win G$. Otherwise, we write $\pl A \notwin G$.
\end{defn}

@@

If we wish to show that a winning strategy does not exist for a player
(i.e. $\pl A\notwin G$), we
often consider an arbitrary legal strategy, and use it to define a legal
\term{counter-attack} for the opponent. If we can prove that the result of
the game for that strategy and counter-attack is a victory for the opponent,
then a winning strategy does not exist.

@@

\begin{proof}
  $\pl A\win \bakergame{\mathbb{R}}$, since $a_n$ must converge to some
  real number. This implies $\pl B\notwin \bakergame{\mathbb{R}}$, and thus
  $\mathbb{R}$ is not countable.
\end{proof}

@@

\begin{thm}
$\pl E\notwin \bmgame{X}$ if and only if $X$ is a Baire space.
\cite{MR0431104}
\end{thm}

### 2014-12-04 phd/dissertation/chapter5.tex
overall cleanup

\begin{thm}
  $\pl K\not\prewin \gruKLGame{\omega\cup\{\mc F\}}$ for any free
  ultrafilter $\mc F$.
\end{thm}

@@

\begin{thm}
  If $\mc F$ is a selective ultrafilter, then
  $\pl K\not\prewin \gruKPGame{\omega\cup\{\mc F\}}$.
\end{thm}

@@

While $\pl O\ktactwin{k+1}\gruConGame{\oneptcomp X}{\infty}$ implies
$\pl O\tactwin\gruConGame{\oneptcomp X}{\infty}$, and likewise for Markov
strategies, this result cannot be
immediately extended to $\gruKPGame{X}$. However, this section will
demonstrate a non-trivial example of a locally-compact space $\pmb X$ for which
$\pl K\win\gruKPGame{\pmb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\pmb X}$
for any $k<\omega$.

@@

\begin{cor}
  There exists a space $X$ such that $\pl K\win\gruKPGame{X}$ but
  $\pl K\not\kmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
\end{cor}

>>>>

\begin{thm}
  $\pl K\notprewin \gruKLGame{\omega\cup\{\mc F\}}$ for any free
  ultrafilter $\mc F$.
\end{thm}

@@

\begin{thm}
  If $\mc F$ is a selective ultrafilter, then
  $\pl K\notprewin \gruKPGame{\omega\cup\{\mc F\}}$.
\end{thm}

@@

While $\pl O\ktactwin{k+1}\gruConGame{\oneptcomp X}{\infty}$ implies
$\pl O\tactwin\gruConGame{\oneptcomp X}{\infty}$, and likewise for Markov
strategies, this result cannot be
immediately extended to $\gruKPGame{X}$. However, this section will
demonstrate a non-trivial example of a locally-compact space $\pmb X$ for which
$\pl K\win\gruKPGame{\pmb X}$ but $\pl K\notkmarkwin{k}\gruKPGame{\pmb X}$
for any $k<\omega$.

@@

\begin{cor}
  There exists a space $X$ such that $\pl K\win\gruKPGame{X}$ but
  $\pl K\notkmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
\end{cor}
